---
title: "DiabetesAssociationRules"
author: "Poonam Sampat"
date: "September 15, 2018"
output: html_document
---

## Used Association Rules, to conclude the important rules that lead to admission for > 30 days, lesser than 30 days and no admissions.
Flow
1.Have created the input as a basket of features.
2.Used support, lift to filter the rules for the categories.
3.Removed any repeatitive rules.


#Install Required Packages.
```{r Packages}
if (!require(Matrix)) {install.packages("Matrix")}
if (!require(arules)) {install.packages("arules")}
if (!require(arulesViz)) {install.packages("arulesViz")}

library("Matrix")
library("arules")
library("arulesViz")
```

## Read the input data as a basket, have created the same using Python.


```{r readFile}
trs <- read.transactions("C:\\Users\\H219960\\Desktop\\Personal\\ISB\\Classes\\Term3\\Pract2\\basket_diab.csv", format = "basket", sep=",")
```

#Rules for greater than 30 days.
Have considered confidence as 50%.

We can see around 5124 rules. 

```{r}
rgrt30.association.rules <- apriori(trs, parameter = list(supp=0.001, conf=0.5),appearance = list(default="lhs",rhs="readmitted>30"))

inspect(head(sort(rgrt30.association.rules, by="lift")))
```
# Are there any redudant rules?
Yes reduced viable rules from around 5128 to 3908!!

Lets understand these rules:
1. No# of emergency visit =1, diag_1=498,Discharged 
2.diag_2=428,timeinhosipital=6,Admission Source = Emergency Room,Admission Type = Urgent
3.diag_1 = 428, diag_2= 491 and a Physician Referral.
4. No# of emergency visit =1,diag_2 = 403,Discharged to home.
5. Age 60-70,Diag_1 =491, Discharged/transferred to home with home health service
```{r}
subset.rules <- which(colSums(is.subset(rgrt30.association.rules, rgrt30.association.rules)) > 1) # get subset rules in vector
length(subset.rules)  

rgrt30.subset.association.rules <- rgrt30.association.rules[-subset.rules] # remove subset rules.

inspect(head(sort(rgrt30.subset.association.rules, by="lift")))
```
#Plotting the data.
```{r}
plot(rgrt30.subset.association.rules)
```
```{r}
plot(rgrt30.subset.association.rules[1:10], method = "graph",  engine = "htmlwidget")
```

#Similar excerise for readmitted<30.
```{r}
rless30.association.rules <- apriori(trs, parameter = list(supp=0.001, conf=0.2),appearance = list(default="lhs",rhs="readmitted<30"))

subset.rules <- which(colSums(is.subset(rless30.association.rules, rless30.association.rules)) > 1) # get subset rules in vector
length(subset.rules)  #> 3913

rless30.association.rules <- rless30.association.rules[-subset.rules] # remove subset rules.

inspect(head(sort(rless30.association.rules, by="lift")))

inspect(rless30.association.rules[1:25])
```

```{r}
Notreadmit.association.rules <- apriori(trs, parameter = list(supp=0.001, conf=0.5,maxlen =3), appearance = list(default="lhs",rhs="Not-readmitted"))

inspect(Notreadmit.association.rules[1:50])

inspect(head(sort(Notreadmit.association.rules, by="lift")))
```

